Article Title

### 2019-08-22 text/03-results.Rmd
Add quality evaluation step

>>>>

```{r quality-table}
dt2 <- read.csv("../analyses/quality/quality_table.csv", header=T)
kable(dt2, booktabs=TRUE, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "SimGIC2 score")) %>%
 kable_styling(latex_options = c("striped")) %>%
 collapse_rows(columns = 1, latex_hline="major")
```
